Paper 2: Vitamin D

### 2017-11-02 doc/vitaminD.Rmd
remove PTH from gee model

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("lVitD", "lPTH"),
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

>>>>

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)
